A Unification of Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-01-06 colt-21/cvx-flats.tex
Took another pass on Theorem 28

@@

@@

	Let us define $\E_p\partial L(u,Y) = \cl(\{\int \nu(y) p(dy) : \nu \in \L^1_d(\A), \nu(y) \in \partial L(u,Y)\,\, a.s.\})$, where $\L^1_d(\A)$ is the set of Lebesgue measurable functions defined on the $\sigma$-algebra $\A$.

@@

	By construction we have $p \in F = \ker(\nu) \cap \P \implies p \in \ker(\nu) \implies \vec 0 = \E_p \nu(Y) \implies \vec 0 \in \E_p \partial L(u,Y) \implies p \in \Gamma_u$.
	Moreover, we $\codim(F) \leq d$ by definition.
%	
%
%	\bigskip
%	
	%Now, it is just left to show that we must have $\Gamma_u \subseteq \gamma_r$.
	%Let $r' = \psi(u)$; by definition of indirect elicitation, we must have $\gamma_{r'} \supseteq \Gamma_r \supseteq F \cap \P$.
	%If $|\gamma(p)| = 1$, then we are done, as we must have $r' = r$ by indirect elicitation.
	%Now if $|\gamma(p)| > 1$ there are two cases.
	%If $r = \psi(u)$, we are trivially done.
	%If $r' = \psi(u) \neq r$, then we seek to show \jessie{help?}	
\end{proof}

>>>>

The proof for Theorem~\ref{thm:cvx-flats} only requires slight modifications for infinite $\Y$; we restate such definitions here and generalize the proof.

@@

We additionally have to generalize the definition of $\E_p \partial L(u,Y)  := \cl(\{\int \nu(y) p(dy) : \nu \in \L^1_d(\A), \nu(y) \in \partial L(u,Y)\,\, a.s.\})$, where $\L^1_d(\A)$ is the set of Lebesgue measurable functions defined on the $\sigma$-algebra $\A$.

@@

@@

	By construction we have $p \in F \implies \int \nu(y) d(py) = \vec 0 \implies \vec 0 \in \E_p \partial L(u,Y) \implies p \in \Gamma_u$.
	Moreover, we $\codim(F) \leq d$ by definition.
%	
%
%	\bigskip
%	
	%Now, it is just left to show that we must have $\Gamma_u \subseteq \gamma_r$.
	%Let $r' = \psi(u)$; by definition of indirect elicitation, we must have $\gamma_{r'} \supseteq \Gamma_r \supseteq F \cap \P$.
	%If $|\gamma(p)| = 1$, then we are done, as we must have $r' = r$ by indirect elicitation.
	%Now if $|\gamma(p)| > 1$ there are two cases.
	%If $r = \psi(u)$, we are trivially done.
	%If $r' = \psi(u) \neq r$, then we seek to show \jessie{help?}	
\end{proof}
